### 2018-08-02 README.Rmd
add scripts README

---
output: github_document
---

@@

## Scripts

The scripts folder contains all the scripts necessary to fully reproduce the benchmarking manuscript in chronologically ordered subfolders. Each subfolder contains a readme file with further explanations of the different scripts and what they do:

```{r}
scripts <- read_rds(derived_file("scripts.rds", experiment_id = "12-varia/01-scripts"))

scripts %>% filter(
  level == 1
) %>%
  arrange(ix) %>%
  mutate(
    name = str_glue("[{id}](https://github.com/dynverse/dynbenchmark/tree/master/{location})"),
    order = ifelse(is.na(ix), "", ix)
  ) %>% 
  select(order, subfolder = name, description = title) %>%
  knitr::kable()

```

>>>>

---
output: github_document
editor_options: 
  chunk_output_type: console
---

@@

```{r child='scripts/README.Rmd'}
```
